Drivers of spatial synchrony in giant kelp populations

### 2021-06-24 paper/SupMat.Rnw
typo

\begin{equation}
\bar \epsilon^{(\dot {EC})} = \bar \epsilon^{(EC)} - \bar \epsilon^{(\ddot {EC})}
\end{equation}

@@

>>>>

\begin{equation}
\bar \epsilon^{(\dot {EC})} = \bar \epsilon^{(EC)} - \bar \epsilon^{( {EC_0})}
\end{equation}

@@

\begin{equation}
\bar \epsilon^{( {EC_0})} = \bar r_1 - \bar r_1^{\#} + \bar r_2^{\#},
\end{equation}

\noindent where $ \bar r_1, \bar r_1^{\#}$ and $\bar r_2^{\#}$ are in the symmetric case. In our model,

\begin{equation}
\bar \epsilon^{( {EC_0})} = \EX(\ln[1-\delta+\delta \exp(u_1)]) - \EX(\ln[1-\delta+\delta \exp(u_1^{\#})]) + \EX(\ln[1-\delta+\delta \exp(u_2^{\#})]),
\end{equation}

\noindent where $u_1 \sim N(\mu_1-\mu_2, 2\sigma^2-2\rho)$, $u_1^{\#} \sim N(\mu_1-\mu_2, 2\sigma^2)$, and $u_2^{\#} \sim N(0, 2\sigma^2)$

\noindent *Note that the contribution of asymmetry to storage effects is not the same as the storage effect that we computed above for asymmetriv cases.

In generalized terms, this further decomposition could be applied to test for contributions of asymmetry between any two variables. Here we tested the asymmetry between $b_1$ and $b_2$. Why did we not look at E and C? Do they have to be normally distrubuted?

This break down would only work if the variables are normally distributed. Thus one can convert their distribution to normal to impliment this decomposition.
